Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-09 paper/main.tex
update figure captions

\begin{table}[t]
    \centering
    \setlength{\tabcolsep}{0.5em} % for the horizontal padding
    {\renewcommand{\arraystretch}{1.2}% for the vertical padding
    \input{tab/arh/binomial}
    }
    \caption{Evaluation metrics for the coverage sets comparing hospitalizations with social burden. In general training on the ODE results in slightly better coverage sets than on the Binomial model. Training on infections (ARI) still provides a competitive coverage set in terms of hospitalizations. All PCN coverage sets outperform the baseline.}
    \label{tab:coverage-set}
  \end{table}

We learn a coverage set that ranges from imposing minimal restrictions to enforcing many restrictions (see Figure~\ref{fig:policy-execution}). The coverage set is shown in Figure~\ref{fig:pf-binomal-arh-budgets}.

@@

\begin{figure}
    \centering
    \input{fig/budget_5}
    \caption{Selection of policies learned by PCN, from most restrictive in terms of social burden (top) to least restrictive (bottom).
    }
    \label{fig:policy-execution}
\end{figure}

>>>>

\begin{table}[t]
    \centering
    \setlength{\tabcolsep}{0.5em} % for the horizontal padding
    {\renewcommand{\arraystretch}{1.2}% for the vertical padding
    \input{tab/arh/binomial}
    }
    \caption{Evaluation metrics for the coverage sets comparing hospitalizations with social burden. In general, an increase of budget results in a better coverage set. Training on infections (ARI) still provides a competitive coverage set in terms of hospitalizations. All PCN coverage sets outperform the baseline.}
    \label{tab:coverage-set}
  \end{table}

We learn a coverage set that ranges from imposing minimal restrictions to enforcing many restrictions (see Figure~\ref{fig:policy-execution}). The coverage set is shown in Figure~\ref{fig:pf-binomal-arh-budgets}. On the right, we display the coverage set of the best-performing run in terms of hypervolume, for each budget setting. On the left, we show an interpolated average of the coverage sets learned by the different runs.

@@

\begin{figure}
    \centering
    \input{fig/budget_5}
    \caption{Selection of policies learned by $\text{PCN}_{b=5}$, from most restrictive in terms of social burden (top) to least restrictive (bottom).
    }
    \label{fig:policy-execution}
\end{figure}
